%%% SVN stuff
\svnid{$Id: KNEAD_STP_Chapter_04_1.tex 153 2025-03-24 15:02:14Z Lewis $}

\input{DIDINFO_Snippets/STP/STP_4.1.0_DIDINFO.tex}

This section provides general and/or common information for all tests.

\subsection{Test Levels}
\label{loc:TestLevels}

\input{SevenStageTestDescriptions.tex}

\subsection{Test Classes}
\label{loc:TestClasses}

Following the seven test stage paradigm, the testing is divided into four classes:
\begin{enumerate}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
	\item {\bf Development Testing} validation of the system components, sub-systems, and system in the development environment, following stages 1-5 above.
	\item {\bf Environmental} validation of the system environmental constraints, following stage 6 above.
	\item {\bf Design Testing} (\StageDT) validation of the system meeting the design specifications, following stage 7 above.
	\item {\bf Operational Testing} (\StageOT) validation of the system meeting the operational goals and mission needs, following stage 7 above.
\end{enumerate}

\subsection{Test Conditions}
\label{loc:TestConditions}

Test conditions will be defined in each test specification (procedure).


\subsection{Test Progression}
\label{loc:TestProgression}

The tests will progress in the general order specified above for the stages.
This is not to say that all stage-1 tests will be completed before any stage-2 testing begins, and so forth.
Additionally, sub-system testing may proceed based on procurement and assembly constraints rather than an order that follows the design hierarchy.
It is expected, however, that all developmental, environmental, and design testing will be completed before the final operational testing commences.

\subsection{Data recording, reduction, and analysis}
\label{loc:DataRecordingReductionAndAnalysis}

Each test will define the data to be recorded.
The test specifications will define the information needed to perform any analysis needed to validate the specifications covered by each test or test case.