%%% SVN stuff
\svnid{$Id: KNEAD_STP_Chapter_04_2_5.tex 153 2025-03-24 15:02:14Z Lewis $}

\input{DIDINFO_Snippets/STP/STP_4.2.0_DIDINFO.tex}

This section defines the plans for the \TestIdNameX validation efforts.

\subsubsection{Test Objective}
\label{loc:TestObjective\TestIdName}

The test objective for \TestIdNameX is to demonstrate operations of the entire \ThisSys, but with some possible limitations.
For example, the entire system may be set up within a laboratory or testbed environment to facilitate \RF communications between nodes and test endpoints instead of final endpoint targets.
The \TestIdNameX may also include noise generators so that communications can be stress-tested to demonstrate it meets specified quality of service levels.
The goal of this testing to to demonstrate that the system functions as expected in as near-to-deployed scenario as is possible, without being a fully deployed configuration.

\subsubsection{Test Level}
\label{loc:TestLevels\TestIdName}

The test level for \TestIdNameX is \StageFive as defined by \citeStageTestingSTD.

\subsubsection{Test Type or Class}
\label{loc:TestType\TestIdName}

The test type or class for \TestIdNameX is development testing.
Note that in this case, this testing may also include validation of system-level external interfaces.

\subsubsection{Qualification Method}
\label{loc:TestQualificationMethod\TestIdName}

The test qualification method for \TestIdNameX is demonstration, inspection, test, or analysis as necessary to ensure each subsystem meets the design specifications.

\subsubsection{Traceability}
\label{loc:TestTraceability\TestIdName}

The test traceability for \TestIdNameX must be included in the overall \RTVM.
For ``Form, Fit, or Function'' testing, the results are expected to map to related operational or interface specifications.
These trace classes are expected to map System/Subsystem Specification (\SSS) implementation requirements to specific tests and/or test cases within a System Test Specification (\STS).

\subsubsection{Special Requirements}
\label{loc:TestSpecialRequirements\TestIdName}

The test special requirements for \TestIdNameX are defined as necessary in test procedures.
Test procedures within an \STS may include references to overall assembly or operational set-up documentation to prevent duplication of information.

\subsubsection{Data Recoding}
\label{loc:TestDataRecoding\TestIdName}

The test data recoding for \TestIdNameX is to record all inspection results in hard copy or electronic form.
Electronic form (e.g., a database application with bar code scanning capability) is preferred, but not required, to minimize labor effort and data entry errors.

\subsubsection{Assumptions or Constraints}
\label{loc:TestAssumptionsOrConstraints\TestIdName}

The test assumptions or constraints for \TestIdNameX are defined in the associated inspection or test procedures.

\subsubsection{Safety, Security, and Privacy}
\label{loc:TestSafetySecurityPrivacy\TestIdName}

The test safety, security, and privacy for \TestIdNameX are defined in the associated inspection or test procedures.
Special care must be taken when test results indicate issues with security measured for the system.

\subsubsection{Tests and Test Cases}
\label{loc:TestsAndTestCases\TestIdName}

Tests and test cases for this test stage are:
\begin{enumerate}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
	
	\item {\bf Functional assessment of system with \TBD.}
	\begin{enumerate}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
		\item {\bf Test Case One} Validation of \TBD.
		\item {\bf Test Case Two} Validation of \TBD.
	\end{enumerate}
	
	\item {\bf \TBD assessment of system with \TBD.}
	\begin{enumerate}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
		\item {\bf Test Case One} Validation of \TBD.
		\item {\bf Test Case Two} Validation of \TBD.
	\end{enumerate}
	
\end{enumerate}
