%%% SVN stuff
\svnid{$Id: KNEAD_STP_Chapter_04_2_7_OT.tex 153 2025-03-24 15:02:14Z Lewis $}

\input{DIDINFO_Snippets/STP/STP_4.2.0_DIDINFO.tex}

This section defines the plans for the \TestIdNameX validation efforts.

\paragraph{Test Objective}
\label{loc:TestObjective\TestIdName}

The test objective for \TestIdNameX is to demonstrate operations of the entire \ThisSys, with all tests performed by an outside agency.
The goal of this testing is to demonstrate that the system functions as expected in a deployed scenario, with all external interfaces being supplied by the actual systems.

\paragraph{Test Level}
\label{loc:TestLevels\TestIdName}

The test level for \TestIdNameX is \StageSeven as defined by \citeStageTestingSTD.

\paragraph{Test Type or Class}
\label{loc:TestType\TestIdName}

The test type or class for \TestIdNameX is operational testing (\StageOT).

\paragraph{Qualification Method}
\label{loc:TestQualificationMethod\TestIdName}

The test qualification method for \TestIdNameX generally is performed via demonstration, but other methods may be performed as necessary to ensure the system meets the operational specifications.

\paragraph{Traceability}
\label{loc:TestTraceability\TestIdName}

The test traceability for \TestIdNameX must be included in the overall \RTVM.

\paragraph{Special Requirements}
\label{loc:TestSpecialRequirements\TestIdName}

The test special requirements for \TestIdNameX are defined as necessary in test procedures.
Test procedures within an \STS may include references to overall assembly or operational set-up documentation to prevent duplication of information.
This testing is expected to be performed by a separate test organization that may prepare its own test procedures based upon the organization's own quality management system and certifications.

\paragraph{Data Recoding}
\label{loc:TestDataRecoding\TestIdName}

The test data recoding for \TestIdNameX is to record all inspection results in hard copy or electronic form.
Electronic form (e.g., a database application with bar code scanning capability) is preferred, but not required, to minimize labor effort and data entry errors.
For tests performed by a separate test organization, they will follow their own processes for data recording and provide records to the development team as appropriate.

\paragraph{Assumptions or Constraints}
\label{loc:TestAssumptionsOrConstraints\TestIdName}

The test assumptions or constraints for \TestIdNameX are defined in the associated inspection or test procedures.
These details are expected to be performed by a separate test organization.

\paragraph{Safety, Security, and Privacy}
\label{loc:TestSafetySecurityPrivacy\TestIdName}

The test safety, security, and privacy for \TestIdNameX are defined in the associated inspection or test procedures.
Special care must be taken when test results indicate issues with security measured for the system.


\subsubsection{Tests and Test Cases}
\label{loc:TestsAndTestCases\TestIdName}

Tests and test cases for this test stage are:
\begin{enumerate}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
	
	\item {\bf \TBD} Operational qualification tests will be determined  by the \StageOT organization.
	%\begin{enumerate}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
		%\item {\bf Radios} Material receipt inspections for all radio devices.
	%\end{enumerate}

\end{enumerate}