%%% SVN stuff
\svnid{$Id: KNEAD_STP_Chapter_04_2_4.tex 153 2025-03-24 15:02:14Z Lewis $}

\input{DIDINFO_Snippets/STP/STP_4.2.0_DIDINFO.tex}

This section defines the plans for the \TestIdNameX validation efforts.

\subsubsection{Test Objective}
\label{loc:TestObjective\TestIdName}

The test objective for \TestIdNameX is to demonstrate operations within a system or sub-system.
For example, a networking sub-system may be validated to ensure configurations are correct and expected throughput capacities are met.
Specialized software or test harnesses may be developed and/or used to perform these tests.
This level of testing ensures that the sub-system meets its external interface definitions and functions as expected before being integrated into a larger system of systems.

\subsubsection{Test Level}
\label{loc:TestLevels\TestIdName}

The test level for \TestIdNameX is \StageFour as defined by \citeStageTestingSTD.

\subsubsection{Test Type or Class}
\label{loc:TestType\TestIdName}

The test type or class for \TestIdNameX is development testing.
Note that in this case, this testing may also include validation of sub-system external interfaces.

\subsubsection{Qualification Method}
\label{loc:TestQualificationMethod\TestIdName}

The test qualification method for \TestIdNameX generally is performed via test, but analysis may be performed as necessary to ensure each subsystem meets the design specifications.

\subsubsection{Traceability}
\label{loc:TestTraceability\TestIdName}

The test traceability for \TestIdNameX generally is included in the overall \RTVM.
For ``Form, Fit, or Function'' testing, the results are expected to map to related operational or interface specifications.
These trace classes are expected to map System/Subsystem Specification (\SSS) implementation requirements to specific tests and/or test cases within a System Test Specification (\STS).

\subsubsection{Special Requirements}
\label{loc:TestSpecialRequirements\TestIdName}

The test special requirements for \TestIdNameX are defined as necessary in test procedures.
Test procedures within an \STS may include references to overall assembly or operational set-up documentation to prevent duplication of information.

\subsubsection{Data Recoding}
\label{loc:TestDataRecoding\TestIdName}

The test data recoding for \TestIdNameX is to record all inspection results in hard copy or electronic form.
Electronic form (e.g., a database application with bar code scanning capability) is preferred, but not required, to minimize labor effort and data entry errors.

\subsubsection{Assumptions or Constraints}
\label{loc:TestAssumptionsOrConstraints\TestIdName}

The test assumptions or constraints for \TestIdNameX are defined in the associated inspection or test procedures.

\subsubsection{Safety, Security, and Privacy}
\label{loc:TestSafetySecurityPrivacy\TestIdName}

The test safety, security, and privacy for \TestIdNameX are defined in the associated inspection or test procedures.
Special care must be taken when test results indicate issues with security measured for the system.

\subsubsection{Tests and Test Cases}
\label{loc:TestsAndTestCases\TestIdName}

Tests and test cases for this test stage are:
\begin{enumerate}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
	
	\item {\bf Power} Functional assessment of power distribution and \UPS capabilities.
	\begin{enumerate}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
		\item {\bf Power Distribution} Validation of power distribution in \ThisSys.
		\item {\bf \UPS} Validation of \UPS in \ThisSys.
	\end{enumerate}
	
	\item {\bf Networking} Functional assessment of network topology and configuration.
	\begin{enumerate}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
		\item {\bf \IP Addressing} Validation of \IPvFour and \IPvSix addressing and routing.
		\item {\bf \NTP Services} Validation of \NTP services.
	\end{enumerate}
	
	\item {\bf Authentication} Functional assessment of user authentication services.
	\begin{enumerate}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
		\item {\bf Setup} Validation of user and group setup from SysAdmin workstations.
		\item {\bf Operations} Validation of operational access from all workstations.
	\end{enumerate}
	
	\item {\bf Radios} Functional assessment of radio configuration and operation.
	\begin{enumerate}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
		\item {\bf Configuration} Validation of configuration control from Maintainer workstations.
		\item {\bf Communication} Validation of operational control from Operator workstations.
		\item {\bf Arbitration} Validation of arbitration control (operator assignment) from Operator workstations.
	\end{enumerate}
	
	\item {\bf Recording} Functional assessment of recording, playback, and offloading capabilities.
	\begin{enumerate}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
		\item {\bf Recording} Validation of voice recording from Operator workstations.
		\item {\bf Playback} Validation of voice playback from Maintainer workstation (\KVM connected to recorder).
		\item {\bf Offloading} Validation of voice offloading from Maintainer workstation (\KVM connected to recorder).
	\end{enumerate}
	
\end{enumerate}