%%% SVN stuff
\svnid{$Id: KNEAD_STP_Chapter_04_2_6.tex 153 2025-03-24 15:02:14Z Lewis $}

\input{DIDINFO_Snippets/STP/STP_4.2.0_DIDINFO.tex}

This section defines the plans for the \TestIdNameX validation efforts.

\subsubsection{Test Objective}
\label{loc:TestObjective\TestIdName}

The test objective for \TestIdNameX is to demonstrate that the system meets special constraints it may endure in a non-operational state (e.g., during transport) or in an operational state once deployed.
This testing may rely on results of Component-Level Special Testing performed during \StageThree testing, as defined in \S~\ref{loc:TestObjectiveStageThree} or it may require retesting of the entire system due to transport or operational constraints.
Testing between these two levels is required to prevent duplicate assessments.

\subsubsection{Test Level}
\label{loc:TestLevels\TestIdName}

The test level for \TestIdNameX is \StageSix as defined by \citeStageTestingSTD.

\subsubsection{Test Type or Class}
\label{loc:TestType\TestIdName}

The test type or class for \TestIdNameX is environmental testing.

\subsubsection{Qualification Method}
\label{loc:TestQualificationMethod\TestIdName}

The test qualification method for \TestIdNameX generally is performed via test, but analysis may be performed as necessary to ensure the system meets the design specifications.

\subsubsection{Traceability}
\label{loc:TestTraceability\TestIdName}

The test traceability for \TestIdNameX must be included in the overall \RTVM.

\subsubsection{Special Requirements}
\label{loc:TestSpecialRequirements\TestIdName}

The test special requirements for \TestIdNameX are defined as necessary in test procedures.
Test procedures within an \STS may include references to overall assembly or operational set-up documentation to prevent duplication of information.
This testing is expected to be performed at a specialized test facility that prepares its own test procedures based upon the facility's own quality management system and certifications.


\subsubsection{Data Recoding}
\label{loc:TestDataRecoding\TestIdName}

The test data recoding for \TestIdNameX is to record all inspection results in hard copy or electronic form.
Electronic form (e.g., a database application with bar code scanning capability) is preferred, but not required, to minimize labor effort and data entry errors.
For tests performed by a specialized test facility, they will follow their own processes for data recording and provide records to the development team as appropriate.

\subsubsection{Assumptions or Constraints}
\label{loc:TestAssumptionsOrConstraints\TestIdName}

The test assumptions or constraints for \TestIdNameX are defined in the associated inspection or test procedures.
These details are expected to be performed at a specialized test facility.

\subsubsection{Safety, Security, and Privacy}
\label{loc:TestSafetySecurityPrivacy\TestIdName}

The test safety, security, and privacy for \TestIdNameX are defined in the associated inspection or test procedures.
Special care must be taken when test results indicate issues with security measured for the system.

\subsubsection{Tests and Test Cases}
\label{loc:TestsAndTestCases\TestIdName}

Tests and test cases for this test stage are:
\begin{enumerate}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
	
	\item {\bf \TBD} Special tests will be determined during the design phase.
	%\begin{enumerate}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
		%\item {\bf Radios} Material receipt inspections for all radio devices.
		%\item {\bf Computers} Material receipt inspections for all computer devices.
		%\item {\bf Network Equipment} Material receipt inspections for all networking devices.
		%\item {\bf Cables} Material receipt inspections for all \COTS cable assemblies.
		%\item {\bf Miscellaneous Equipment} Material receipt inspections for all miscellaneous electronics devices.
	%\end{enumerate}

\end{enumerate}
