%%% SVN stuff
\svnid{$Id: SVD_Chapter_03.tex 126 2024-07-14 03:51:40Z KneadProject $}

\chapter{Version Description}
\label{loc:VersionDescription}
% \input{DIDINFO_Snippets/SVD/SVD_3.0.0_DIDINFO.tex}
This chapter provides an output of how version control works.

\section{Inventory of Materials}
\label{loc:InventoryOfMaterials}
% \input{DIDINFO_Snippets/SVD/SVD_3.1.0_DIDINFO.tex}
\begin{center}
\begin{tabular}{|| c c c c c c c ||}
\hline
 ID & Titles & Abrv & Dates & Version & Release & Description\\
\hline 
\hline
 ID1 & Buying hardware & BS & 09/17/2015 &  V1.0.0 & 0 & Just purchased the STM32 board\\ 
\hline
\end{tabular}
\end{center}

\section{Inventory of Software}
\label{loc:InventoryOfSoftware}
% \input{DIDINFO_Snippets/SVD/SVD_3.2.0_DIDINFO.tex}
\begin{center}
\begin{tabular}{|| c c ||}
\hline
 Software Name & Description \\
\hline 
\hline
 Mbed Studio & Deployed code to the STM32 board\\
 Visual Studio Code & Writing the codebase in this editor \\
 Github & Includes Version Source Control and Pipline Jobs \\
\hline
\end{tabular}
\end{center}

\section{Changes From Prior Version}
\label{loc:ChangesFromPriorVersion}
% \input{DIDINFO_Snippets/SVD/SVD_3.3.0_DIDINFO.tex}

\begin{center}
\begin{tabular}{|| c c c c c c c ||}
\hline
 ID & Titles & Abrv & Dates & Version & Release & Description\\
\hline 
\hline
 ID1 & Basic setup & BS & 09/17/2015 &  V1.0.0 & 0 & Initial design\\ 
\hline
\end{tabular}
\end{center}

\section{Adaptation Data}
\label{loc:AdaptationData}
% \input{DIDINFO_Snippets/SVD/SVD_3.4.0_DIDINFO.tex}

The version sets up an system will have a bare minimum approach. Just to have basic functionality. 

\section{Related (Third Party) Documents}
\label{loc:RelatedDocuments}
% \input{DIDINFO_Snippets/SVD/SVD_3.5.0_DIDINFO.tex}

Currently there are no third party artifacts that we need for this project.
\begin{center}
\begin{tabular}{|| c c c c c c c ||}
\hline
 ID & Titles & Abrv & Dates & Version & Release & Description\\
\hline 
\hline
\hline
\end{tabular}
\end{center}

\section{Installation Instructions}
\label{loc:InstallationInstructions}
% \input{DIDINFO_Snippets/SVD/SVD_3.6.0_DIDINFO.tex}
\begin{itemize}
    \item First connect board to laptop directly through micro-usb. 
    \item Using the embed studio IDE (this might change to use Keli Studio) identify which chip by connecting to it. 
    \item Once the code is up and running then deploy to it.
\end{itemize}

\section{Possible Problems and Known Errors}
\label{loc:PossibleProblemsAndKnownErrors}
% \input{DIDINFO_Snippets/SVD/SVD_3.7.0_DIDINFO.tex}
The system is not completely working. There would be problems when running the system.