%%% SVN stuff
\svnid{$Id: About_SSDD_Artifacts.tex 126 2024-07-14 03:51:40Z KneadProject $}

\subsection{Artifact Format}
\label{loc:DocOverview_ArtifactFormat}
\DIDINFO{This paragraph shall summarize the purpose and contents of this document and shall describe any security or privacy considerations associated with its use.}

This document format is based upon the guidance in the \SSDD{} \DID~\cite{ref__SSDD_DID}.
The system design is documented following the guidelines of ISO-12207~\cite{ref__ISO_12207} and MIL-STD-498~\cite{ref__MIL_STD_498} (from which ISO-12207 originated).
The goal of this artifact is to provide a road map to the design implementation through either linkage to the development items (for example code, hardware, and \CAD drawings) or, for larger systems, segregated documentation such as Software Design Description (\SDD), Hardware Design Description (\HWDD), or Interface Design Description (\IDD) artifacts.
This document follows the listed \SSDD sub-section order.
\begin{description}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
	\item[Section 1] provides an overview of the system and this document.
	\item[Section 2] lists general and application-specific reference documents as well as glossary terms and acronyms. 
	\item[Section 3] presents the system-wide design decisions.
	\item[Section 4] provides the detailed system architecture design. 
	\item[Section 5] provides any applicable requirement traceability.
	\item[Appendices] if needed, provide additional information as may be needed.
\end{description}

\input{DIDINFO_Snippets/DIDINFOoverview.tex}
