%%% SVN stuff
\svnid{$Id: About_SDP_Artifacts.tex 126 2024-07-14 03:51:40Z KneadProject $}

\subsection{Artifact Format}
\label{loc:DocOverview_ArtifactFormat}
\DIDINFO{This paragraph shall summarize the purpose and contents of this document and shall describe any security or privacy considerations associated with its use.}

This document format is based upon the guidance in the \SDP{} \DID~\cite{ref__SDP_DID}.
The specifications and associated acceptance criteria are documented following the guidelines of ISO-12207~\cite{ref__ISO_12207} and MIL-STD-498~\cite{ref__MIL_STD_498} (from which ISO-12207 originated).

This document is a short description of the design documentation philosophy for this project.
The normal \SDP format is not followed.
Instead, most of the \SDP information is expected to reside within the developer's \QMS.
This artifact provides a condensed version of the \SDP to capture information directly relevant to this development effort, such as tools, repository information, and 

%%%Some information provides general details about the format of this specification document.
%%%This information, such as formatting details, is common across all levels of specification documents.
%%%Other information is specific to this particular document.
%%%This information is provided to assist the reader in understanding the format and layout of the information contained in this document.
%%%

This document is divided into the following major sections.
\begin{description}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
	\item[Section 1] provides an overview of the system and this document.
	\item[Section 2] lists general and application-specific reference documents as well as glossary terms and acronyms. 
	\item[Section 3] outlines the required work for this development effort.
	\item[Section 4] summarizes the overall development plans.
	\item[Section 5] outlines the system transition plans.
	\item[Section 6] describes the management and control activities for the development effort.
	\item[Appendices] provide details, as may be needed, regarding the usage of the system.
\end{description}

\input{DIDINFO_Snippets/DIDINFOoverview.tex}
