%%% SVN stuff
\svnid{$Id: About_CMPLAN_Artifacts.tex 126 2024-07-14 03:51:40Z KneadProject $}

\subsection{Artifact Format}
\label{loc:DocOverview_ArtifactFormat}
\DIDINFO{This paragraph shall summarize the purpose and contents of this document and shall describe any security or privacy considerations associated with its use.}

This document format is based upon the guidance in the \CMPLAN \DID~\citeIEEEstdCM, but may be tailored to reflect current quality management system (\QMS) or other program requirements.
This \CMPLAN also follows the guidelines of ISO-12207~\cite{ref__ISO_12207} and MIL-STD-498~\cite{ref__MIL_STD_498} (from which ISO-12207 originated).
It is expected that significant content of the \CMPLAN may be references to external \QMS, \CMMI, or other related documentation.
Thus, agencies using this artifact may formalize it to serve as a checklist for tailoring each effort per their own processes and procedures.

This tailoring also includes planning for \CM aspects as may be needed for the complete system development efforts.
The \CMPLAN \DID mainly covered \CM of software.
This artifact includes sections that cover the development of hardware as well as software, firmware, and the environment itself.
Integration and testing are also included, since the tools and environment need to be under \CM.
The organization is such that unneeded sections can be omitted as needed.

This document follows a tailored \CMPLAN sub-section order of:
\begin{description}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
	\item[Section 1] provides an overview of the system and this document.
	\item[Section 2] lists general and application-specific reference documents as well as glossary terms and acronyms. 
	\item[Section 3] summarizes the required planning for teh \CM effort for the project.
	\item[Section 4] defines the organization, roles, and responsibilities.
	\item[Section 5] identifies the configuration items for the
		\begin{itemize}[topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
			\item Development Environment,
			\item Documentation, and
			\item System Components.
		\end{itemize}
	\item[Section 6] defines the Change Management steps of the
		\begin{itemize}[topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
			\item Baseline Process,
			\item Change Process,
			\item Process Accounting,
			\item Process Auditing, and
			\item Process Tools.
		\end{itemize}
	\item[Section 7] if needed, lists any general notes as may be applicable.
	\item[Appendices] if needed, provide additional information as may be needed.
\end{description}

\input{DIDINFO_Snippets/DIDINFOoverview.tex}
