%%% SVN stuff
\svnid{$Id: SPS-SSS_SpecificationFormatting.tex 139 2025-06-13 20:26:50Z KneadProject $}

\subsection{Specification Formatting}
\label{loc:Intro_SpecFormatting}

\input{AboutArtifacts/SPS-SSS_SpecificationFormatting_NoRefToHowToSections.tex}


External tools have been written that allow for automatic generation of other documentation.
Specially, data for chapters and appendices that follow the requirement specifications, can be gleaned automatically to ensure integrity between the sections of the documents.
In addition, the listing of \KPP and \KSA values into a ``B-spec'' can be automated.
Finally, the full set of requirements, and the associated attributes, are exported to a comprehensive \CSV file for import into \MBSE tools such as \DOORS or \CAMEO.


This table approach offers other advantages besides automated parsing for import into tools.
As can be seen in Table~\ref{rqt:TableFormat}, and in all the specifications, this format groups all information for each specification into a separable and easily viewed structure.
The document sections and subsections provide a logical grouping of the specifications but the table allows all pertinent information to be grouped, vice being split across major sections of the document.
This grouping allows for easier presentation since each grouping is similar to a ``PowerPoint'' presentation slide.
And, as will be seen in Section~\ref{loc:Intro_HowToReadSpecifications}, it can help the writer organize specifications.
The approach also allows for a ``List of Specifications'' to be generated.
Each table is listed in the list of specifications so that each high level grouping can be quickly located from the list.
Of course, the tables are located in the appropriate sections as noted in Section~\ref{loc:DocOverview_ArtifactFormat} so they can be found in that manner as well.


Another major advantage of the table format is the ``Notes'' section.
As specifications are developed, there will be many issues to be resolved.
And, once issues are clarified, tracking the rationale for the decision is just as important as recording the answer~\cite{ref__Brooks_MMM}.
Thus the notes section helps the reader and the writer.
The writer has a logically grouped place to put notes for each specification and the reader can easily find them without having to refer to footnotes, separated sections, or external documentation.

