%%% SVN stuff
\svnid{$Id: SDP_Chapter_04.tex 126 2024-07-14 03:51:40Z KneadProject $}

\chapter{System Development Plans}
\label{loc:PlansForSystemDevelopment}
% \input{DIDINFO_Snippets/SDP/SDP_4.0.0_DIDINFO.tex}

This chapter is \TBD.

\section{Hardware Development Plans}
\label{loc:SDP_HardwareDevelopmentPlans}
% \input{DIDINFO_Snippets/SDP/SDP_4.1.0_DIDINFO.tex}

% This section is \TBD.
The System will not need additional hardware for completion of work. If additional features are needed then this section shall be updated.

\section{Firmware Development Plans}
\label{loc:SDP_FirmwareDevelopmentPlans}
% \input{DIDINFO_Snippets/SDP/SDP_4.2.0_DIDINFO.tex}

% This section is \TBD.
This System would require new updates to the firmware. Most firmware update is caused because of different packages that would update the middleware on the system.
To keep the system up to date. Every release would have a tag to which firmware released.


\section{Software Development Plans}
\label{loc:SDP_SoftwareDevelopmentPlans}
% \input{DIDINFO_Snippets/SDP/SDP_4.3.0_DIDINFO.tex}

% This section is \TBD.
The design shall be written as a uml format. Then would have a top down design.

\section{Integration Plans}
\label{loc:SDP_IntegrationPlans}
% \input{DIDINFO_Snippets/SDP/SDP_4.4.0_DIDINFO.tex}

% This section is \TBD.
Currently, the plan is the update to the system through STLink. The STLink should be used to used to flash the system and debug the system.


\section{Testing Plans}
\label{loc:SDP_TestingPlans}
% \input{DIDINFO_Snippets/SDP/SDP_4.5.0_DIDINFO.tex}

% This section is \TBD.
To keep a CICD pipeline structure, there shall be an automated process to build and test my code. As code get developed and processed every merge into a codebase.


\section{Other Development Activities}
\label{loc:SDP_OtherDevelopmentActivities}
% \input{DIDINFO_Snippets/SDP/SDP_4.6.0_DIDINFO.tex}

This section is \TBD.