%%% SVN stuff
\svnid{$Id: KNEAD_CMPLAN_Chapter_05_Docs.tex 126 2024-07-14 03:51:40Z KneadProject $}

\section{Documentation}
\label{loc:CI_Documentation}

This section lists the system documentation items that have configurations that must be managed.

\subsection{Management}
\label{loc:CI_System_Management}

This section lists the project management items that have configurations that must be managed.

\subsection{Model}
\label{loc:CI_System_Model}

This section lists the software items that have configurations that must be managed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% These sections assume the documentation items are delivered in phases
% For CDS devices going through an LBSA, there are five (5) phases
% For CDS devices going through an SBSA, there are four (4) phases
% Tailor these phases accordking to what makes sense for the project at hand
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{LBSA}
\label{loc:CI_Docs_LBSA}

This section lists the documents delivered, or produced by an external agency, for each \LBSA phase.

\subsubsection{Phase 1}
\label{loc:CI_Docs_LBSA_Phase1}

This section lists the \CDS \LBSA Phase-1 documentation items that have configurations that must be managed.

\subsubsection{Phase 2}
\label{loc:CI_Docs_LBSA_Phase2}

This section lists the \CDS \LBSA Phase-2 documentation items that have configurations that must be managed.

\subsubsection{Phase 3}
\label{loc:CI_Docs_LBSA_Phase3}

This section lists the \CDS \LBSA Phase-3 documentation items that have configurations that must be managed.

\subsubsection{Phase 4}
\label{loc:CI_Docs_LBSA_Phase4}

This section lists the \CDS \LBSA Phase-4 documentation items that have configurations that must be managed.

\subsubsection{Phase 5}
\label{loc:CI_Docs_LBSA_Phase5}

This section lists the \CDS \LBSA Phase-5 documentation items that have configurations that must be managed.


\subsection{SBSA}
\label{loc:CI_Docs_SBSA}

This section lists the documents delivered, or produced by an external agency, for each \SBSA phase.

\subsubsection{Phase 1}
\label{loc:CI_Docs_SBSA_Phase1}

This section lists the \CDS \SBSA Phase-1 documentation items that have configurations that must be managed.

\subsubsection{Phase 2}
\label{loc:CI_Docs_SBSA_Phase2}

This section lists the \CDS \SBSA Phase-2 documentation items that have configurations that must be managed.

\subsubsection{Phase 3}
\label{loc:CI_Docs_SBSA_Phase3}

This section lists the \CDS \SBSA Phase-3 documentation items that have configurations that must be managed.

\subsubsection{Phase 4}
\label{loc:CI_Docs_SBSA_Phase4}

This section lists the \CDS \SBSA Phase-4 documentation items that have configurations that must be managed.
