%%% SVN stuff
\svnid{$Id: KNEAD_CMPLAN_Chapter_05_DevEnv.tex 126 2024-07-14 03:51:40Z KneadProject $}

\section{Development Environment}
\label{loc:CI_Environment}

This section lists the development environments that have configurations that must be managed.
These lists include items such as tools used for design, compilation, and debugging of \MBSE models, software, hardware, testing, documentation, and such.

\subsection{Equipment}
\label{loc:CI_Dev_Equipment}

This section lists the environment's equipment items, such as the network devices and general monitoring systems, such as \SIEM tools, that have configurations that must be managed.

\subsubsection{Infrastructure}
\label{loc:CI_Dev_Infrastructure}

This section lists the infrastructure items (routers, switches, cabling, etc.) that have configurations that must be managed.

\subsubsection{Monitoring}
\label{loc:CI_Dev_Monitoring}

This section lists the monitoring items (\SIEM, access control, etc.) that have configurations that must be managed.


\subsection{Modeling Tools}
\label{loc:CI_Dev_Modeling}

This section lists the model development environment items that have configurations that must be managed.

\subsection{Software Tools}
\label{loc:CI_Dev_Software}

This section lists the software development environment items that have configurations that must be managed.

\subsection{Firmware Tools}
\label{loc:CI_Dev_Firmware}

This section lists the firmware development environment items that have configurations that must be managed.

\subsection{Hardware Tools}
\label{loc:CI_Dev_Hardware}

This section lists the hardware development environment items that have configurations that must be managed.

\subsection{Integration Tools}
\label{loc:CI_Dev_Integration}

This section lists the integration environment items that have configurations that must be managed.

\subsection{Test Tools}
\label{loc:CI_Dev_Test}

This section lists the test environment items that have configurations that must be managed.

\subsection{Production Tools}
\label{loc:CI_Dev_Production}

This section lists the production environment items that have configurations that must be managed.

\subsection{Documentation Tools}
\label{loc:CI_Dev_Documentation}

This section lists the documentation generation items that have configurations that must be managed.


